---
title: "Report on the first name MARIE"
author: "your name here"
date: "September 2023"
output: 
  html_document:
    theme: cosmo
  
---
### 1. Setup
The packages needed in an Rmd must *always* be loaded in a code chunk at the beginning of the file
```{r, message = F}
library(dplyr)
library(ggplot2)
```
However, the command `install.packages()` must **not** be written in an R Markdown. It should be run only once in the console. 

### 2. Data cleaning
```{r, results = 'hide'}
names <- read.csv("../data/03_fichier_prenoms.csv", sep = ";", encoding = "UTF-8") %>% 
  mutate(sex = ifelse(sexe == 1, "Male", "Female")) %>% 
  rename(year = annais, births = nombre, name = preusuel) %>% 
  filter(year != "XXXX") %>% 
  mutate(year = as.numeric(year))
```

### 3. Evolution of the first name MARIE over time 
```{r}
names %>% 
  filter(name == "MARIE") %>% 
  ggplot(aes(x = year, y = births,
             color = sex)) +
  geom_line()
        
```

`r sum(names[names$name== "MARIE" & names$year == 2021, "births"])` children were born under the name MARIE in 2021. This statistic is written in **inline code** so it updates automatically. 

